Reading Notes

### 2020-09-01 reading-notes.tex
replaced all missing citations
writing. filling in gaps
new papers

\cite{Mazzio2015}

@@

\cite{Berendsen2010}

@@

>>>>

\cite{Mazzio2015} **

@@

\cite{Berendsen2010} *

@@

\cite{Gao2020}
polymer solar cells with nonfullerene acceptors - analysing morphology formation of nonfullerene/polymer cells with effective polymer thermodynamic quantity: Flory-Huggins interaction parameter.
>1000 NFAs
they cite a material getting over 18\% PCE?? refs 13,14
good starting point is miscibility
(flory huggins is related to miscibility but takes into account size differences between polymer/solvent)
this metric is useful for narrowing down what might be a good solar cell

\cite{Lee2020}
solvent evaporation study using MD
explicit solvent is removed intermittently from far above the surface to mimic the open air
this is different than other simulations where a solvent molecule was removed at random
they want to see the effects of concentration gradients
They see that some solvent molecules are trapped in the film and many species move less (based on MSD) as the ismulation progresses
